---
title: "Writing Functions"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(rvest)

knitr::opts_chunk$set(
	echo = TRUE,
	fig.height = 6,
	fig.width = 8,
	warning = FALSE,
	out.wideth = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))

set.seed(1)
```


## Get start

we are going to write some functions

calculating z-scores

```{r}
x = rnorm(n = 30, mean = 4, sd = 2.3)
x_again = rnorm(n = 30, mean = 6, sd = 0.3)

(x - mean(x)) / sd(x)
(x_again - mean(x_again)) / sd(x_again)
```

Now a function

```{r}
z_score = function(x_arg) {
  (x_arg - mean(x_arg)) / sd(x_arg)
}
```

Try the function

```{r, error=TRUE}
z_score(x_arg = x_again)
z_score(x_arg = 3)
z_score(x_arg = "my name is jeff")
z_score(x_arg = c(TRUE, TRUE, FALSE, TRUE))
```

Here, we receive a lot errors when using the functions. Thus, we want to add some conditions to our fucntion. 

```{r}
z_score = function(x_arg) {
  
  if (!is.numeric(x_arg)) {
    stop("x should be numeric")
  } else if (length(x_arg) == 1) {
    stop("x should be larger than 3")
  }
  
  (x_arg - mean(x_arg)) / sd(x_arg)
  
}
```

Try the function again

```{r, error=TRUE}
z_score(x_arg = x_again)
z_score(x_arg = 3)
z_score(x_arg = "my name is jeff")
z_score(x_arg = c(TRUE, TRUE, FALSE, TRUE))
```


## Multiple outputs

```{r}
mean_and_sd = function(input_x) {
  
  if (!is.numeric(input_x)) {
    stop("x should be numeric")
  } else if (length(input_x) == 1) {
    stop("x should be larger than 3")
  }
  
  list(
    mean_input = mean(input_x),
    sd_input = sd(input_x),
    z_score = (input_x - mean(input_x)) / sd(input_x)
  )
  
}
```

test the function

```{r}
mean_and_sd(input_x = x)
```


## Multiple inputs

```{r}
set.seed(1)
sim_data = tibble(
  x = rnorm(30, mean = 1, sd = 1),
  y = 2 + 3 * x + rnorm(30, 0, 1)
)

# check the data I created
sim_data %>% ggplot(aes(x = x, y = y)) + geom_point()

# do a linear regression analysis
ls_fit = lm(y ~ x, data = sim_data)
  
beta0_hat = coef(ls_fit)[1]
beta1_hat = coef(ls_fit)[2]
```

the chunk of the code above is kind of redundant and not tidy, let's use a function

```{r}
set.seed(50)

sim_regression = function(n, beta0, beta1) {
  sim_data = tibble(
    x = rnorm(n, mean = 1, sd = 1),
    y = beta0 + beta1 * x + rnorm(n, 0, 1)
  )

  ls_fit = lm(y ~ x, data = sim_data)
  tibble(
    beta0_hat = coef(ls_fit)[1],
    beta1_hat = coef(ls_fit)[2]
  )
}

sim_regression(30, 2, 3)
```


## scrape the Amazon

```{r}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

dynamite_html = read_html(url)

review_titles = 
  dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-title") %>%
  html_text()

review_stars = 
  dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text()

review_text = 
  dynamite_html %>%
    html_nodes(".review-text-content span") %>%
    html_text()

reviews = tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text
)
```

this chunk of the code that get the information of page 1. But what if I want the info from page 2,
page3? Now, let's use a function!

```{r}
read_page_reviews <- function(url) {
  
  h = read_html(url)
  
  review_titles = h %>%
    html_nodes("#cm_cr-review_list .review-title") %>%
    html_text()
  
  review_stars = h %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text() %>%
    str_extract("\\d") %>%
    as.numeric()
  
  review_text = h %>%
    html_nodes(".review-data:nth-child(4)") %>%
    html_text()
  
  tibble(
    title = review_titles,
    stars = review_stars,
    text = review_text
  )
}
```

```{r}
read_page_reviews(url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=2")
```








